\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{S.}
\familyname{Khalymon}
\address{}{Kyiv, Ukraine}
\mobile{+38 097 773 69 47}
\email{sergiykhalimon@gmail.com}
\homepage{https://www.linkedin.com/in/serhii-khalymon-38044b56/}
% \extrainfo{Software should be beautiful. Both inside and outside.}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
	\maketitle
	
	\section{Career Summary}
	\cvline
	{}
	{I have about 5+ years of commercial Python development experience. My strong sides are analytical, problem-solving and communication skills. \newline{}}


	\section{Commercial Projects}
	\cvline
	{Applitools Mar 2018 - present}
	{\url{https://github.com/applitools/eyes.selenium.python}\newline{}
	\url{https://github.com/applitools/eyes.sdk.python}\newline{}
	    AI powered end-to-end visual testing \& monitoring.\newline{}
        Responsibilities:
            \begin{enumerate}
                \item supporting and improving existing SDK, creating new SDK;
                \item writing tests and automated test framework;
                \item reading of Java, Ruby, C# and JS SDK's;
                \item verification of errors from customers;
                \item architecture creation and implementation;
                \item debugging and fixing platform specific bugs;
                \item design of client API and code refactoring.
            \end{enumerate}
		\newline{}\newline{}
		Python 2.7/Python 3.7, multithreading, multiprocessing, pytest, mock, invoke, namespaces packages, selenium, attrs, Pillow, transitions, appium, travis-ci, android and ios emulators, tinycss2}

	\cvline
	{Fundedbyme Jun 2016 - Mar 2018}
	{\url{https://fundedbyme.com}\newline{}
		Crowdfunding for intelligent growth.\newline{}
        Responsibilities:
            \begin{enumerate}
                \item clarification of the specification;
                \item feature leading;
                \item mentoring;
                \item code review;
                \item support existing and write new functionality.
            \end{enumerate}
		\newline{}\newline{}
		Python 2.7, Django, PostgreSQL, AWS, Ansible, Fabric, nosetests, Jira, Intercom API, Sendgrid, REST}

	\cvline
	{Khai \& Kharkiv-vodokanal  Feb 2016 - Jun 2016}
    {Designing of the client-server service for monitoring and control of inspectors for entrepreneur consumers.\newline{}
    Responsibilities:
        \begin{enumerate}
            \item build the development team;
            \item write specification;
            \item draw use cases diagram;
            \item decompose user stories to tasks;
            \item communication with customer;
            \item design server-mobile communication protocol.
        \end{enumerate}
    \newline{}\newline{}
    Asana, UML, JSON-RPC, Postgresql, PHP, Java(Android)}

	\cvline
	{Ambiencedata May 2014 - Nov 2016}
	{\url{http://ambiencedata.com}\newline{}
		Ambience Data air monitoring system provides quick access to accurate data about the air quality within a local area.\newline{}
		Responsibilities: 
		    \begin{enumerate}
		        \item clarification of the specification;
		        \item design UI/UX;
		        \item design and develop DB structure;
		        \item develop scraper for parsing and storing data from several weather resources;
		        \item develop REST API for geo data;
		        \item develop word map with bunch of layers which contains information about weather and pollutants;
		        \item develop API for consuming and display charts from our devices.
		    \end{enumerate}
		\newline{}\newline{}
		Python 2.7, Django, PostgreSQL, Leaflet, Google Charts, Scrapy, Asana, Google Map API, Memcached, Redis, Celery}


	\section{Non-commercial Projects}
    Below present not a full list of projects. Some projects exists in private repos. All projects designed and built by me from scratch.

	\subsection{JavaScript}
	\cvline
	{AllatRa Live\\ Jun 2019 - present}
	{\url{https://live.allatra.tv}\newline{}
		Streaming platform for simultaneous interpretation.\newline{}
		ReactJs, amplitudejs, mobx, classes, icecast, nginx, nginx-rtmp, ansible}
	
	\subsection{Rust}
    \cvline
	{Firefox starter\\ Sep 2017 - Oct 2017}
	{\url{https://github.com/skhalymon/firefox_starter}\newline{}
		Firefox profiles manager allowing to start few instances of browser.\newline{}
		GTK-RS}

	\subsection{Python}
	\cvline
	{ephyr-control\\ Jun 2020 - present}
	{\url{https://github.com/ALLATRA-IT/ephyr-control}\newline{}
		Client library that allow to control \href{https://github.com/ALLATRA-IT/ephyr}{Ephyr} streaming. \newline{}
		Python 3.7+, pydantic, zmq}
	\cvline
	{facecast-io\\ Feb 2020 - present}
	{\url{https://github.com/ALLATRA-IT/facecast-io}\newline{}
		Unofficial API client to \url{https://facecast.io} service. \newline{}
		Python 3.7+, poetry, typer, pydantic, httpx}
	\cvline
	{annots\\ Dec 2016}
	{\url{https://github.com/skhalymon/annots}\newline{}
		annots is the package that allow to use Python 3.6 variable annotations in handy way.\newline{}
		Python 3.6}
	\cvline
	{Epubsearcher\\ Mar 2015 - Jan 2016}
	{\url{https://github.com/skhalymon/epubsearcher}\newline{}
		Library for search selected words in Epub publications.\newline{}
		Python 3.4, Beatifulsoup4, lxml, Whoosh}
	\cvline
	{AllatRa Encyclopedy\\ Jun 2015 - Dec 2015}
	{\url{https://github.com/skhalymon/wiki-and-reader}\newline{}
	    Website that gives you opportunity read books with annotations
		with articles from encyclopedia. \newline{}
		Python 3.4, Django, Celery, MySql, Ansible, epubsearcher...}
    \cvline
	{ec315 status app indicator\\ Jul 2014}
	{\url{https://github.com/skhalymon/ec315-status-app-indicator}\newline{}
		Gnome Applet Indicator for Huawei ec315 modem. Displays signal strength, allows and to change connection mode and reboot modem.\newline{}
		Python 2.7, PyGTK }
	\cvline
	{Polls post\\ Aug 2014}
	{\url{https://github.com/skhalymon/polls_post}\newline{}
		App for posting to VK communities. Can work with few accounts.\newline{}
		Python 2.7, PyQt, VK Api}

	\section{Development skills}
	\subsection{Programming and Markup Languages}
	\cvline{Advanced level}
	{Python}
    \cvline{Mid-level}
    {JavaScript, HTML}
    \cvline{Basic level}
    {Java, SASS, CSS, Rust, PL/SQL, Bash, LaTeX}
	\cvline{Reading level}
	{Ruby, C\#, C, PHP}

	\section{Server administration skills}
	\cvline
	{Server management with}{Terraform, Ansible, Fabric}
	\cvline
	{Deployment to}{Heroku, Dokku, OpenShift, GAE, AWS}
	\cvline
	{Write configs for}{Nginx, Gunicorn, uWSGI, SystemD services, Vagrant, Docker, icecast, nginx-rtmp, ffmpeg}
	
	\section{Computer skills}
	\cvline
	{IDE/Editors}{PyCharm, WebStorm, IntellliJ, RubyMine, Rider, Android Studio, XCode, VS Code, Sumblime Text, Vim}
	\cvline
	{OS}{Linux (Ubuntu, Debian, Arch), Windows 10, Windows Server 2016, macOS}
	\cvline
	{VCS}{Git}

	\section{Languages Proficiency level}
	\cvline
	{Native}{Russian, Ukrainian}
	\cvline
	{Intermediate}{English}
	
	\section{Education}
	\cventry
	{Sep 2012 - Jan 2017}
	{Computer Engineering}
	{National Aerospace University -'Kharkiv Aviation Institute' ,Ukraine}
	{}{}{}
	{Sep 2008 - Jun 2012}
	{Computer Engineering}
	{College of Sumy State University, Konotop, Ukraine.}
	{}{}{}
	\cventry
	
	\section{Courses}
	\cvline
	{Cisco Networking Academy}{CISCO IoT}
	\cvline
	{INTUIT}{\href{https://www.intuit.ru/verifydiplomas/00187814}{Linux Administration}}
	\cvline
	{University of Alberta}{\href{https://coursera.org/share/5eb676b588d0e8d5bbc77f3a6707afb7}{Object-Oriented Design}, Design Patterns, Software Architecture, Service-Oriented Architecture}
	
	\section{Public activity}
	\cvline{LinkedIn}{\url{https://www.linkedin.com/in/serhii-khalymon-38044b56/}}
	\cvline{GitHub}{\url{https://github.com/skhalymon}}
\end{document}
